Verifying Demonstrations

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md

Reviewer 1

1)
a) Therefore anonymous credentials and unlinkability properties: the central authority cannot tell participants from non-participants without extreme measures which are equivalent to arresting people at the protest. Arguably, the chilling effects with this system are no more than that of protests alone already.

b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias. Those who verify results must apply the standard source criticism. e.g. as for detecting bias in scientific research.

2) Petitions have been viable for a long time, but people arrange protests anyway. Our scheme allows for both anonymous verifiable petitions (skip location) and protests (time and location matter).

3) Agreed, but we need all parts.

4) Agreed, we need to present the adversaries better. A2 was to show limitations. Grace can already now make examples of people; crocus cannot make physical protests safer, we only want to not make it worse.

5) That’s the reason for distance bounding. Then any witness will know that it’s within a given distance from the witness’ own position. Why a verifier accepts this is up to the trust assumptions: we give two cases, the verifier trusts the particular witness; or the verifier “trusts” that a threshold of witnesses is probably true.

6) Trusted by a verifier. Anyone can define whom they trust and how they counted. We _do_ use trusted witnesses for counting.

7) Strength: yes.

Reviewer 2

Definitions not entirely formal: working on it.

Single participant gathering proof shares for friends: The distance bounding prevents this being done by relaying messages. The terrorist-fraud assumption from distance bounding also prevents giving the private key (or phone containing it) to someone: the private keys are part of the long-term ID credential, if this ID can be used for other things, as pointed out by Reviewer 1, then you will not allow just anyone to use it.

Reviewer 3)

1) Yes, following the standard assumption in distance bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).  We will look into the possibilities of functional encryption, that might actually violate the terrorist-fraud assumption.

2) This extreme case where no type of wireless communication works, not even the short range needed here, is possible but not heard of. Perhaps NFC could help.

3) No principled way given online mobs, but different counts are possible and as long as the parameters are published, the counts can be verified. Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the eyes of the verifier.

4) 5G is built for scale but currently not for the D2D scenario; again, NFC is 
an option.

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md

Reviewer 2

Definitions not entirely formal: working on it.

Single participant gathering proof shares for friends: The distance bounding prevents this being done by relaying messages. The terrorist-fraud assumption from distance bounding also prevents giving the private key (or phone containing it) to someone: the private keys are part of the long-term ID credential, if this ID can be used for other things, as pointed out by Reviewer 1, then you will not allow just anyone to use it.

Reviewer 3

1) Yes, following the standard assumption in distance bounding to prevent 
terrorist fraud (which is distance-bounding terminology for this particular 
case).

Functional encryption will not work against an honest verifier in the general 
case. We are working on a distance bounding protocol (it requires a separate 
paper) and in that scheme the private key can be computed by joining two 
different outputs from the functional encryption of the private key. Hence it's 
reduced to the terrorist-fraud case again.

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md

6) Trusted by a verifier. Anyone can define whom they trust and how they counted. We _do_ use trusted witnesses for counting.

7) Strength: yes.

Reviewer 2

Definitions not entirely formal: if there are specific parts that should be more formalized, we'll be happy to work on that.

@@

Functional encryption will not work against an honest verifier in the general 
case. We are working on a distance bounding protocol (it requires a separate 
paper) and in that scheme the private key can be computed by joining two 
different outputs from the functional encryption of the private key. Hence it's 
reduced to the terrorist-fraud case again.

2) This extreme case where no type of wireless communication works, not even the short range needed here, is possible but not heard of. Perhaps NFC could help.

3) No principled way given online mobs, but different counts are possible and as long as the parameters are published, the counts can be verified. Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the eyes of the verifier.

4) 5G is built for scale but currently not for the D2D scenario
without provider; again, NFC is an option. For overall performance, we
could evaluate AnonPass on phones, example distance-bounding
computation, collect density and scalability from the literature
(protests and wireless), and measure NFC delays, if you deem it
useful.

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md

Reviewer 1

1) a) Due to the use of anonymous credentials, the central authority cannot tell participants from non-participants without extreme measures equivalent to arresting people at the protest. Arguably, the chilling effects with this system are no more than that of "standard" protests. To mitigate the risk of having a central authority responsible the IDs, we could also replace it by a distributed version composed of several independent entities that simulate the work of the central authority is a distributed and private manner.

b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias. In particular, those who verify results must apply the standard source criticism. (e.g., for detecting bias in scientific research).

2) Petitions have been viable for a long time but people still arrange protests anyway, in part because going physically to a protest in a sense shows much more involvment. Our scheme allows for both anonymous verifiable petitions (not considering location) and protests (time and location matter).

3-4) We acknowledge that the design of the architecture is complex but we need all parts to reach the desired security and privacy properties. To improve the clarity of the paper, we agree that we need to present the adversaries better. The objective of introducing A2 was to show the limitations of our approach. While Crocus cannot make physical protests safer, we wanted to ensure that it does make it worse.

5) This is the main reason for distance-bounding as it allows the witness to verify that it is within a given distance from the prover.  Why a verifier accepts this claim is up to the trust assumptions for which we provide two cases. One in which the verifier trusts a particular witness and the other in which the verifier believes that a threshold of witnesses has been reached.

6) Trusted by a verifier. Anyone can define whom they trust and how they want to be counted. We _do_ use trusted witnesses for counting.

@@

7) Strength: yes.

Reviewer 2

If there are specific parts that should be more formalized, we will be happy to do this in the revised version of the paper.

With respect to a single participant gathering proof shares for friends, distance-bounding prevents this to be done by relaying messages. In addition, the terrorist-fraud assumption also prevents a user giving his private key (or phone containing it) to someone. This is realistic in scenario in which the private keys are part of the long-term ID credential. In particular as pointed out by reviewer 1 if this ID can be used for other things, you will not allow just anyone to use it.

Reviewer 3

1) Yes, it follows the standard assumption in distance-bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).

Functional encryption will not work against an honest verifier in the general case. We are working on a distance-bounding protocol (in preparation for a separate paper) in which the private key can be computed by joining two different outputs from the functional encryption of the private key, which reduced to the terrorist-fraud case again.

2) This extreme case in which no type of wireless communication works is possible but unheard of. However, it could be potentially solve by using NFC capabilities for instance.

3) There is principled way given online mobs, but different counts are possible. As long as these parameters are published, the counts can be verified. Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the verifier's eyes.

4) 5G is built for scale but currently not for the D2D scenario without provider but again NFC is an option. For overall performance, we could evaluate AnonPass on phones, example distance-bounding computation, collect density and scalability from the literature (protests and wireless), and measure NFC delays, which we could do if deemed useful by the reviewers.

### 2019-01-11 paper/reviews/popets-2019.3-rebuttal.md

Reviewer 1

1) a) Due to the use of anonymous credentials, the central authority cannot 
tell participants from non-participants without extreme measures equivalent to 
arresting people at the protest. Arguably, the chilling effects with this 
system are no more than that of "standard" protests.

To mitigate the risk of having a central authority responsible the IDs, we 
could also replace it by a distributed version composed of several independent 
entities that simulate the work of the central authority in a distributed and 
private manner.

b) Yes, but the paper also notes that those are detectable and should be 
ignored due to their obvious bias. In particular, those who verify results must 
apply standard source criticism. (c.f., detecting bias in scientific research).

@@

2) Petitions have been viable for a long time but people still arrange protests 
anyway, in part because going physically to a protest in a sense shows much 
more involvment. Our scheme allows for both anonymous verifiable petitions (not 
considering location) and protests (time and location matter).

3-4) We acknowledge that the design of the architecture is complex but we need 
all parts to reach the desired security and privacy properties. To improve the 
clarity of the paper, we agree that we need to present the adversaries better. 
The objective of introducing A2 was to show the limitations of our approach. 
While CROCUS cannot make physical protests safer, we wanted to ensure that it 
does make it worse.

5) This is the main reason for distance-bounding as it allows the witness to 
verify that it is within a given distance from the prover.  Why a verifier 
accepts this claim is up to the trust assumptions for which we provide two 
cases. One in which the verifier trusts a particular witness and the other in 
which the verifier believes that collusion beyond a threshold is not likely.

@@

7) Strength: yes.

Reviewer 2

If there are specific parts that should be more formalized, we will be happy to 
do this in the revised version of the paper.

With respect to a single participant gathering proof shares for friends, 
distance-bounding prevents this. In addition, the terrorist-fraud assumption 
also prevents a user giving his private key (or phone containing it) to 
someone. This is realistic in scenario in which the private keys are part of 
the long-term ID credential. In particular as pointed out by reviewer 1 if this 
ID can be used for other things, you will not allow just anyone to use it.

@@

Reviewer 3

1) Yes, it follows the standard assumption in distance-bounding to prevent 
terrorist fraud (which is distance-bounding terminology for this particular 
case).

Functional encryption will not work against a verifier who performs the 
distance-bounding. We are working on a distance-bounding protocol (in 
preparation for a separate paper) in which the private key can be computed by 
joining two different (required) outputs from the functional encryption of the 
private key, the terrorist-fraud assumption prevents this.

2) This is an extreme case: it's possible that an adversary can jam signals for 
wireless communication, but it's unheard of. However, it could be potentially 
mitigated by using e.g. NFC.

@@

3) There is principled way given online mobs, but different counts are 
possible. As long as these parameters are published, the counts can be 
verified. Requests for sizeable collusion are made in public, which risk being 
found by the verifier --- thus invalidating the count in the verifier's eyes.

4) 5G is built for scale but currently not for the D2D scenario without 
provider, but again NFC is an option. For overall performance, we could 
evaluate AnonPass on phones, example distance-bounding computation, collect 
density and scalability from the literature (protests and wireless), and 
measure NFC delays, which we could do if deemed useful by the reviewers.

### 2019-01-11 paper/reviews/popets-2019.3-rebuttal.md

1) a) Due to the use of anonymous credentials, the central authority cannot 
tell participants from non-participants without extreme measures equivalent to 
arresting people at the protest. Arguably, the chilling effects with this 
system are no more than that of "standard" protests.

To mitigate the risk of having a central authority responsible the IDs, we 
could also replace it by a distributed version composed of several independent 
entities that simulate the work of the central authority in a distributed and 
private manner.

b) Yes, but the paper also notes that those are detectable and should be 
ignored due to their obvious bias. In particular, those who verify results must 
apply standard source criticism. (c.f., detecting bias in scientific research).

2) Petitions have been viable for a long time but people still arrange protests 
anyway, in part because going physically to a protest in a sense shows much 
more involvement. Our scheme allows for both anonymous verifiable petitions 
(not considering location) and protests (time and location matter).

### 2019-02-05 paper/location-proofs.tex

One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location. \PRIVO shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

>>>>

One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location. \CROCUS shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property. \sonja{any more differences to ours, relevance of this one?} \sonja{add something on platin.io, details unknown but roughly relying on witnesses and graph theory (unique big cluster, assumption of honest majority)}

### 2019-02-05 paper/privacy-analysis.tex

Likewise, thanks to the constraints in the time-stamp granularity,
\(t\) is not unique.

>>>>

Since \(\pid\) uniquely identifies \(P\), then if \(t_s^{(\pid)}\) is 
\enquote{unique enough}\footnote{%
  This can be verified thanks to \cref{CountOnce}.
  If there are no tuples \((\pid, t_s)\) and \((\pid, t_s')\) among the proof 
  shares such that \(\pid \neq \pid'\) but \(t_s = t_s'\), then \(t_s\) also 
  \emph{likely} uniquely identifies \(P\).
  \enquote{Likely} depends on the likelihood of there being witnesses who are 
  not protesters.
}, every \(\wid\) for which \(t_s' = t_s^{(\pid)}\) is \emph{likely} to be 
\(P\) acting as a witness.
This would allow \cref{in-system-adversary} to link \(\wid, \wid'\) for 
different protesters, thus violating \cref{WitnessUnlink}.
(The same can be said of \(\pid\) and \cref{ProtestUnlink} if there are 
multiple protests, \ie \(\cid\)'s, at the same time and location.
However, we deem this as unlikely.)

Distribution of \(t_s\) depends on the rate of \(\TSget\) and the distribution 
of when participants run the algorithm the last time.
For example, if we use a six-hour interval and a rate of one new value per 
minute, then there are potentially 21600 unique values for \(t_s\).
However, we can scale this down by a factor \(n\) by requiring \(\TSget\) to 
use only every \(n\)th block from the underlying ledger.
Thus it seems reasonable that \(t_s\) will never be \enquote{unique enough}.
